## Response variables

```{r setup, include=FALSE, cache=FALSE}
#Set root directory to R project root
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```


details new on markdown


Below are the instructions and code for getting data from wildtrax that was developed by Elly Knight. The original rScripts are available [here](https://github.com/baynelab-research/aru-data-processing-code).

*See the wildRtrax article here for more details on authentication:* <https://abbiodiversity.github.io/wildRtrax/articles/authenticating-into-wt.html>

### Get data from WildTrax

1.  **Load packages**

```{r eval=FALSE}

#install.packages("remotes")
#remotes::install_github("ABbiodiversity/wildRtrax")
library(wildRtrax)
library(tidyverse)
```

2.  **Login to WildTrax**

NOTE: Edit the 'loginexample.R' script to include your WildTrax login details and rename to 'login.R'. DO NOT PUSH YOUR LOGIN TO GITHUB

```{r eval=FALSE}
config <- "login.R"
source(config)

wt_auth()
```

3.  **Get list of projects from WildTrax**

```{r eval=FALSE}
projects <- wt_get_download_summary(sensor_id = 'ARU')
```

4.  **Download RUGR dataset summary report**

```{r eval=FALSE}
dat.rugr <- wt_download_report(project_id = 1321, sensor_id = 'ARU', weather_cols = T, report = "summary")
```

5.  **Download RUGR task report to check coordinate buffering**

```{r eval=FALSE}
task.rugr <- wt_download_report(project_id = 1321, sensor_id = 'ARU', report = "task")
table(task.rugr$buffer)
```

6.  **Download multiple projects**

```{r eval=FALSE}
projects.test <- sample_n(projects, 3)

dat.list <- list()
error.log <- data.frame()
for(i in 1:nrow(projects.test)){
  
  dat.list[[i]] <- try(wt_download_report(project_id = projects.test$project_id[i], sensor_id = projects.test$sensorId[i], weather_cols = F, report = "summary"))
  
  print(paste0("Finished dataset ", projects.test$project[i], " : ", i, " of ", nrow(projects.test), " projects"))
  
}

dat.test <- do.call(rbind, dat.list)
```

7.  **Save with metadata & timestamp**

```{r eval=FALSE}
save(dat, projects.test, error.log, file=paste0("Data/wildtrax_raw_", Sys.Date(), ".Rdata"))
```
